### 2024-01-02 documentation/thesis/thesis_declaration.tex
more thesis

I hereby declare that I have prepared this thesis independently and
without outside assistance. Text passages, which are based literally or
in the sense on publications or lectures of other authors, are marked as
such. The work has not yet been submitted to any other examination
authority and has not yet been published.

>>>>

Hiermit versichere ich, dass ich die vorliegende Arbeit selbstständig
verfasst und keine anderen als die im Literaturverzeichnis angegebenen
Quellen benutzt habe. Stellen, die wörtlich oder sinngemäß aus
veröffentlichten oder noch nicht veröffentlichten Quellen entnommen
sind, sind als solche kenntlich gemacht. Die Zeichnungen oder
Abbildungen in dieser Arbeit sind von mir selbst erstellt worden oder
mit einem entsprechenden Nachweis versehen. Diese Arbeit ist in gleicher
oder ähnlicher Form noch bei keiner anderen Prüfungsbehörde eingereicht
worden.

I hereby certify that I have written this thesis independently and have
not used any sources other than those listed in the bibliography. Any
passages taken verbatim or in spirit from published or unpublished
sources are labelled as such. The drawings or illustrations in this work
have been created by myself or have been labelled accordingly. This
thesis has not been submitted in the same or a similar form to any other
examination authority.

### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  State of the art
\item
  Usecases
\item
  Unified Sensor
\item
  Software readout framework
\item
  Usability improvements
\item
  Evaluation
\end{enumerate}

@@

@@

\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mrpcli_config_rest]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]

   # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
   $ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
   {
   "output":[
      "2"
   ]
}
}
\end{lstlisting}

@@

@@

\begin{lstlisting}[language=Python]
from MRP import MRPAnalysis
from MRP import MRPDataVisualization
# Create a empty reading with no settings. Only the raw values are needed, no metadata
reading = MRPReading.MRPReading()
# CREATE A SAMPLE MEASUREMENT
for i in range(1000):
    measurement = MRPReadingEntry.MRPReadingEntry()
    # readout sensor or use dummy data and assign result
    measurement.value = (random.random() -0.5) * 2
    reading.insert_reading_instance(measurement, False)

# PLOT MEAN VISUALIZATION
MRPDataVisualization.MRPDataVisualization.plot_error([reading])
# APPLY COMPENSATION
# Here the ``calculate_mean`` function is used
# see MRPAnalysis module for alternatives
reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
# we want to subtract the mean value from all readings
reading_mean_value = -reading_mean_value
# modify measurement values
MRPAnalysis.MRPAnalysis.apply_global_offset_inplace(reading, reading_mean_value)
\end{lstlisting}

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
contains the generated \passthrough{\lstinline!OpenSCAD!}
sourcecode\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}.

@@

\begin{lstlisting}[language=Python, caption={Python docstring example}, label=lst:pydocstring]
    # MRPDataVisualisation.py - example docstring
    def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
        """
        Plots a temperature plot of the reading data as figure
        :param _readings: readings to plot
        :type _readings: list(MRPReading.MRPReading)
        :param _title: Title text of the figure, embedded into the head
        :type _title: str
        :param _filename: export graphic to an given absolute filepath with .png
        :type _filename: str
        :returns: returns the abs filepath of the generated file
        :rtype: str
        """
        if _readings is None or len(_readings) <= 0:
            raise MRPDataVisualizationException("no readings in _reading given")
        num_readings = len(_readings)
        # ...
\end{lstlisting}

>>>>

This work is divided into six main chapters, which deal with the
approach and implementation. The techniques and concepts used are
explained in detail. Specific examples provide an overview of the
possible use of the developed solution by the user.

\ref{state-of-the-art}. \textbf{State of the art} describes the current
state of technology and forms the basis for further development.
Existing measurement methods and findings are shown here in order to
define the context for the current project.

\ref{usecases}. \textbf{Usecases} are the application cases in which the
project is to be used. They illustrate the practical scenarios and
define how the product can be used in the real world. This is crucial
for understanding the needs of the target group and designing the end
result accordingly.

\ref{unified-sensor}. \textbf{Unified Sensor} refers to the integration
of different sensors into a standardised solution. This enables simple
data acquisition and serves as a basic hardware system on which the
subsequent data processing library can be applied.

\ref{software-readout-framework}. \textbf{Software readout framework}
chapter describes the implementation of the data readout framework. This
includes an explanation of the various modules and specific application
examples.

\ref{usability-improvements}. \textbf{Usability improvements} refers to
measures to improve user-friendliness. This involves optimising
interfaces, interactions and processes to ensure intuitive and efficient
use of the product. This includes, code documentation or the
distribution of source code to users.

\ref{evaluation}. \textbf{Evaluation} comprises the systematic review
and assessment of the overall system. This includes the demonstration of
the implemented capabilities of the overall system against the
previously defined use cases.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
\end{enumerate}

@@

\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mrpcli_config_rest]
# GET PROXY STATUS
$ wget http://proxyinstance.local:5556/proxy/status
{
"capabilities":[
  "static",
  "axis_b",
  "axis_x",
  "axis_y",
  "axis_z",
  "axis_temp",
  "axis_stimestamp"
],
"commands":[
  "status",
  "initialize",
  "disconnect",
  "combinedsensorcnt",
  "sensorcnt",
  "readsensor",
  "temp"
]}
# RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
$ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
{
"output":[
  "2"
]}
\end{lstlisting}

@@

\hypertarget{mrpreading}{%
\subsection{MRPReading}\label{mrpreading}}

\begin{lstlisting}[language=Python]
from MRP import MRPReading, MRPMeasurementConfig
# [OPTIONAL] CONFIGURE READING USING MEASUREMENT CONFIG INSTANCE
config: MRPMeasurementConfig = MRPMeasurementConfig
config.sensor_distance_radius(40) # 40mm DISTANCE BETWEEN MAGNET AND SENSOR
config.magnet_type(N45_CUBIC_12x12x12) # CHECK MRPMagnetTypes.py FOR IMPLEMENTED TYPES
# CREATE READING
reading: MRPReading = MRPReading(config)
# ADD METADATA
reading.set_name("example reading")
## ADD FURTHER DETAILS
reading.set_additional_data("description", "abc")
reading.set_additional_data("test-number", 1)
# INSERT A DATAPOINT
measurement = MRPReadingEntry.MRPReadingEntry()
measurement.value = random.random()
reading.insert_reading_instance(measurement, False)
# USE MEASURED VALUES IN OTHER FRAMEWORKS / DATAFORMATS
## NUMPY
npmatrix: np.ndarray = reading.to_numpy_matrix()
## CSV
csv: []= reading.to_value_array()
## JSON
js: dict= reading.dump()
# EXPORT READING TO FILE
reading.dump_to_file("exported_reading.mag.json")

# IMPORT READING
imported_reading: MRPReading = MRPReading()
imported_reading.load_from_file("exported_reading.mag.json")
\end{lstlisting}

\hypertarget{mrphal}{%
\subsection{MRPHal}\label{mrphal}}

\begin{lstlisting}[language=Python]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_serial_ports()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("/dev/serial/by-name/UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

\hypertarget{mrpsimulation}{%
\subsection{MRPSimulation}\label{mrpsimulation}}

\begin{lstlisting}[language=Python]
from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
# GENERATE SILUMATED READING USING A SIMULATED HALLSENSOR FROM magpy LIBRARY
reading: MRPReading = MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
# GENERATE A FULLSPHERE MAP READING
reading_fullsphere: MRPReading = MRPSimulation.generate_random_full_sphere_reading()
# RENDER READING TO FILE IN 3D
visu = MRPPolarVisualization(reading)
visu.plot3d(None)
visu.plot3d("simulated_reading.mag.png")
# EXPORT READING
reading.dump_to_file("simulated_reading.mag.json")
\end{lstlisting}

@@

\begin{lstlisting}[language=Python]
from MRP import MRPAnalysis, MRPDataVisualization, MRPReading
# CREATE EMPTY READING
reading = MRPReading.MRPReading()
# CREATE A SAMPLE MEASUREMENT
for i in range(1000):
    measurement = MRPReadingEntry.MRPReadingEntry()
    # readout sensor or use dummy data and assign result
    measurement.value = (random.random() -0.5) * 2
    reading.insert_reading_instance(measurement, False)
# PLOT MEAN VISUALIZATION
MRPDataVisualization.MRPDataVisualization.plot_error([reading])
# APPLY COMPENSATION
# Here the ``calculate_mean`` function is used
reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
# we want to subtract the mean value from all readings
reading_mean_value = -reading_mean_value
# modify measurement values
MRPAnalysis.MRPAnalysis.apply_global_offset_inplace(reading, reading_mean_value)
\end{lstlisting}

\hypertarget{mrpvisualisation}{%
\subsection{MRPVisualisation}\label{mrpvisualisation}}

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
contains the module generated. After computing the model using the
\passthrough{\lstinline!OpenSCAD!}-\gls{cli} utility, the following
model
rendering\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
can be generated.

@@

\begin{lstlisting}[language=Python, caption={Python docstring example}, label=lst:pydocstring]
# MRPDataVisualisation.py - example docstring
def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
  """
  Plots a temperature bar graph of the reading data entries as figure
  :param _readings: readings to plot
  :type _readings: list(MRPReading.MRPReading)
  :param _title: Title text of the figure, embedded into the head
  :type _title: str
  :param _filename: export graphic to an given absolute filepath with .png
  :type _filename: str
  :returns: returns the abs filepath of the generated file
  :rtype: str
  """
  if _readings is None or len(_readings) <= 0:
      raise MRPDataVisualizationException("no readings in _reading given")
  num_readings = len(_readings)
  # ...
\end{lstlisting}
